Jean Pockets and Gender

### 2024-04-22 paper/paper.qmd
update

---
title: "Jean Pockets and Gender"
subtitle: "subtitle"
author: Hari Lee Robledo
thanks: "Code and data are available at: https://github.com/hari-lr/pockets-and-gender"
date: today
date-format: long
abstract: "Fashion has long reflected and reinforced gender inequalities, with women's clothing often lacking functional pockets found in men's garments. A 2018 study by Jan Diehm & Amber Thomas on The Pudding revealed this discrepancy, highlighting inferior pocket functionality in women's jeans. This paper aims to reproduce these findings and explore if gender disparities extend to pricing. Using the same data, we analyze the correlation between prices of men's and women's jeans. Results suggest that women's jeans not only have smaller pockets but also tend to be more expensive. This study sheds light on gender inequalities in everyday products and their broader implications. [UPDATE]"
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

library(tidyverse)
```

@@

## CSV Dataset and cleaning
Explain how the data was collected and measured

@@

# Model
[TBD]

## Model set-up
## Model justification

>>>>

---
title: "Jean Pockets and Gender"
subtitle: "subtitle"
author: Hari Lee Robledo
thanks: "Code and data are available at: https://github.com/hari-lr/pockets-and-gender"
date: today
date-format: long
abstract: "Fashion has long reflected and reinforced gender inequalities, with women's clothing often lacking functional pockets found in men's garments. A 2018 study by Jan Diehm & Amber Thomas on The Pudding revealed this discrepancy, highlighting inferior pocket functionality in women's jeans. This paper aims to reproduce these findings and explore if gender disparities extend to pricing. Using the same data, we analyze the correlation between prices of men's and women's jeans. Results suggest that women's jeans not only have smaller pockets but also tend to be more expensive. This study sheds light on gender inequalities in everyday products and their broader implications. [UPDATE according to findings]"
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

library(tidyverse)
library(tibble)
library(ggplot2)
library(dplyr)
library(janitor)
library(kableExtra)

## read in cleaned data 
cleaned_pockets_data = read_csv(
  file = here::here("data/analysis_data/cleaned_pockets_data.csv"),
  show_col_types = FALSE
)

## read in cleaned data 
cleaned_pocket_area_data = read_csv(
  file = here::here("data/analysis_data/cleaned_pocket_area_data.csv"),
  show_col_types = FALSE
)
```

@@

## CSV Dataset and cleaning
Explain how the data was collected and measured.

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-cleaned_pockets_data
#| tbl-cap: Sample of Cleaned Pockets Data

# Code referenced from: https://github.com/InessaDeAngelis/Toronto_Elections/blob/main/outputs/paper/toronto_elections_paper.qmd

head (cleaned_pockets_data, 5) |>
  kable(
    col.names = c("brand","style","men_women","price"),
  booktabs = TRUE
  )
```

@@
